\input{1-preamble}
\author{Hannah Jakob Barrett}
\begin{document}
\maketitle

\textit{This pre-analysis plan has been prepared for the Information from Abroad Workshop. Please do not cite or circulate this early draft. I look forward to receiving your comments, especially on the design and case selection. The plan is to submit the questionnaire to the survey company by the end of April.} 

\section{Introduction}
Coercion is a widely studied phenomenon in international relations. In conflict scenarios, coercive threats are designed to elicit a state's desired outcomes by dangling the threat of harm, which manipulates the risk associated with defiance. \textcite{schelling_arms_1966} originally theorized that coercive threats can be either deterrent or compellent; deterrent threats aim to stop an adversary from acting, while compellent threats aim to force them to change course. Moreover, \textcite{schelling_arms_1966} explicitly theorizes that it is much harder to coerce a state into action, thus changing the status quo, than it is to deter an action and preserve the status quo. 

Experimental research has corroborated Schelling's claim that compellent threats suffer from lower credibility and lower success rates than deterrent threats. On the one hand, compellent threats might be written off as cheap talk, or be perceived to be exaggerative. \autocite{fearon_domestic_1994, snyder_cost_2011} In such cases, insights from political psychology have found that compellent threats often backfire, producing reactance, anger, and greater support for defiance of the threat. \autocite{schaub_deterrence_2004, powers_psychology_2023}  On the other hand, by requiring the target state to publicly accept a loss, compellent threats can activate concerns about national reputation and honor, causing even greater support for escalation.\autocite{dafoe_coercion_2021, dafoe_provocation_2022}

I argue that the experimental literature on coercion suffers from limitations that systematically bias it toward finding evidence of failure. The first limitation is one of sample selection. The majority of survey experiments on coercion have been conducted on American respondents. \footnote{\citeauthor{dafoe_provocation_2022}'s study on China is an exception.} Studying the effects of coercive threats on public audiences in military superpowers has clear consequences for both theorizing the mechanisms of coercion and finding generalizable evidence of how coercion operates in the real world. With relative power on their side, respondents in strong states are more likely to interpret adversary threats as bluffs, more likely to abhor reputational losses, and more likely to react defiantly. When the adversary's threats are more likely to be dismissed, compliance with coercive threats is the least likely outcome by design. Generalizing from US samples to a broader population of states that may realistically face coercive threats is therefore problematic, given that most states in the international system are not military superpowers. 

Given the predominance of US-samples, this literature has also not explored how asymmetric threats shape the perceived risk of retaliation. Unilaterally defying coercive threats from an adversary is a privilege of strong states; states facing adversaries with clear military superiority face a fundamentally different risk calculus. I wish to explore whether support for retaliation decreases as power asymmetry increases in the adversary's favor. This constitutes the first contribution of this study. 

Moreover, for states that lack relative military advantages, the availability and commitment of allied support is essential for responding to coercive threats as well as engaging in deterrence. To my knowledge, this mechanism has been largely ignored in the literature on coercion, provocation, and resolve. Thus, I propose to study a second and underexplored factor shaping public responses to coercive threats is whether the target state can count on the support of its allies. Allied support has been shown to deter threats from adversaries and may also embolden target states to retaliate against adversaries when they can rely on military backing. \autocite{fang_concede_2014, benson_inducing_2014} However, the emboldening effect of allied support may be suppressed when facing threats from a more powerful adversary, especially if the public is risk averse.  

I also expect that the effect of alliance support and power asymmetry will be heterogeneous across individuals with different foreign policy orientations. While hawks are theoretically more predisposed to support retaliation, doves are more likely to oppose it. This is in keeping with Kertzer and Brutger's seminal findings that predispositions are predictive of the costs the public tends to place on leaders who threaten force in conflict scenarios. \autocite{kertzer_decomposing_2016, brutger_dispositional_2018} I acknowledge this distinction, but I argue that hawks are also likely to be sensitive to changes in relative power. While we may expect hawkish respondents to be the most reactive and defiant to threats, their support for retaliation may be suppressed when the adversary is clearly more capable and their allies don't have their backs. 

In this pre-analysis plan, I propose a 3 x 2 survey experiment that varies two features of the coercive context: the relative military power of the adversary issuing the threat (stronger, equal to, or weaker than the target state) and whether the target state has the unified backing of its allies. I measure support for retaliation as the primary outcome, making my study comparable to those that have found evidence of coercive failure in US (and Chinese) samples \autocite{dafoe_coercion_2021, dafoe_provocation_2022, powers_psychology_2023}. Unlike these studies, I also leverage pre-treatment measures of foreign policy orientations to test whether the effectiveness of coercion varies systematically between hawks and doves. I theorize that backlash to coercive threats is most probable when the adversary is weak and the target has allied backing, and least probable when power asymmetry is high and the target is forced to stand alone.

The pre-analysis plan centers around the following research questions: 
\begin{enumerate}
    \item \textbf{Do threats from a more powerful adversary decrease support for retaliation against coercive threats?}
    \item \textbf{Does the presence of allied support increase support for retaliation against coercive threats?}
\end{enumerate}

\section{Why Does Coercion Fail...and When Should We Expect it to Succeed?}
%Sechser: yes, the conventional wisdom is that military powers are better...but this ignores reputation
The logic behind my contribution is that states with military advantages are better equipped to make effective, compellent threats. However, \textcite{sechser_goliaths_2010} argues that threatening the weaker David can actually make a fool out of Goliath. Even states with relative power advantages may fail to make effect coercive threats because compliance creates steep reputation costs for the target state, which it may be unwilling to pay if it believes that the adversary will simply continue to make threats. This face-saving mechanism is not confined to the strategic calculations of state leaders; work by Allan Dafoe and coauthors has also found evidence of reputational concerns at the level of public opinion. In two studies, \textcite{dafoe_coercion_2021, dafoe_provocation_2022} demonstrate that coercive threats activate reputational concerns among ordinary citizens, increasing public support for retaliation as a means of protecting national honor. Taken together, these findings suggest that compellent threats may increase the likelihood of retaliation by increasing reputational costs. 

\textcite{powers_psychology_2023} used reactance theory from psychology to argue why the public reacts angrily and defiantly against actions that threaten their country's freedom to make choices. If the public in a target state perceive threats to be constraining and coercive, they will resist, leading to higher support for retaliation as a form of defiance.\autocite{powers_psychology_2023} This evidence isolates reactance to autonomy infringement as a unique psychological mechanism that is distinct from reputational or honor based mechanisms.\autocite{dafoe_coercion_2021, dafoe_provocation_2022}. The positive effect of coercive threats on support for retaliation also appears to be mediated by anger. This is in keeping with research that has found anger to motivate harsher retaliation against terrorism,\autocite{shandler_cyber_2021, fisk_emotions_2019} and anxiety or fear to be associated with a more cautious approach.\autocite{huddy_threat_2005} Studies from this literature have found that weak threats provoke less backlash and are perceived as less credible than stronger, more explicit threats \autocite{lupton_threat_2024}. 

However, \textcite{powers_psychology_2023} acknowledge that coercive threats could actually suppress public support for retaliation if the public perceives the adversary's threat to be a costly signal of resolve. This has yet to be tested in a literature dominated by survey research on US samples, where in the eyes of the American public, global adversaries (real or fictional) are likely to appear weaker and less capable than the US military. If, however, the public perceives coercive threats from a larger power to be a credible signal of resolve, we should expect support for retaliation to be suppressed. 

I argue that when an adversary is substantially more powerful \textbf{and} the target state lacks allied backing, the risks associated with defiance may be high enough to suppress the face-saving mechanism. In fact, this study is designed to test how these two factors interact to shape how the public perceives the risk of retaliation in interstate disputes. The following section elaborates on the ways in which alliances may embolden targets to retaliate, and the conditions under which that effect may be mitigated.  

\section{Does Allied Support Increase Support for Retaliation?}
Military alliances are traditionally understood to have a deterrent value. By providing members with the promise of military support, alliances intend to deter the likelihood of external threats by challenger states.\autocite{johnson_alliance_2023, benson_inducing_2014} Empirical work has also shown that public defense commitments from allies make states less likely to be targets of threats and violence.\autocite{leeds_alliances_2003, fang_concede_2014} At the level of public opinion, alliances have been shown to have a positive effect on public support for military intervention, when an ally faces external threats \autocite{tomz&weeks2021, tomzNATO2023} Alliances do this by creating formal commitments, such as mutual defense agreements, and by establishing a moral relationship between states, in which concerns for loyalty drive public willingness to support allies. 

%except those that argue for a restraining effect!
While allies can increase the resolve of target states by promising their military support, allies may also exert a restraining effect on the target's ability to escalate. If two states engage in a dispute, an ally observing from the sidelines may recommend that the target defy the adversary's demand and reassure the target of continued military support, thereby emboldening the target to retaliate by reducing the risks. \autocite{fang_concede_2014} In other cases, the ally may recommend that the target concede to the adversary's threat. In this case, alliances are expected to have a restraining effect, forcing the target state to concede to the challenger’s threat in order to preserve positive alliance relations.\autocite{fang_concede_2014} 

To date, there are very few tests of the emboldening versus restraining effect of alliances on public opinion. An experimental study by \textcite{kudo_does_2026} did not find evidence of the emboldening effect in Japan. Instead, the authors found that US commitments of military support to back up Japan in a dispute with China did not increase the Japanese public's support for retaliation. However, there a few caveats. The experimental treatment, despite including both verbal and material commitments of US support for Japan, generated very small increases in Japanese confidence that the US would actually intervene on their behalf. Moreover, despite most respondents ranking US military power as superior to that of China (the adversary), the experiment was unable to account for the interaction between power asymmetry and allied support. In a dispute between Japan and China, there is a clear power asymmetry in China's favor. Despite power parity between the US and China, I argue that any emboldening effect of allied support will be suppressed when threats originate from a more powerful adversary, especially if the public is risk averse.  

\section{Which Factors Influence The Perceived Risk of Retaliation?}
Resolve refers to a state's willingness to follow through on threats, even when doing so is costly. It is the difference between bluffing and making a credible threat that is taken seriously by receivers. Resolve is thus a valuable form of information that conveys the risks of refusing to comply with an adversary's threats. \autocite{schelling_arms_1966} A rich literature has applied both qualitative and quantitative approaches to studying resolve, and most importantly for this study, how resolve is perceived by the public. 

In a conjoint experiment, \textcite{kertzer_how_2021} asked respondents to assess a pair of countries involved in a dispute, and evaluate the likelihood that each country would stand firm. The authors found that public perceptions of resolve are primarily driven by four factors: the relative military capabilities of the state, the stakes involved in the dispute, the costly signals the adversary has sent, and whether it backed down or stood firm in prior conflicts. Unsurprisingly, states with powerful militaries are perceived as being more likely to stand firm, especially when the stakes are high. Making a public threat and mobilizing troops constituted an indicator of higher resolve, as did the reputation for standing firm. With a similar conjoint design, \textcite{lupton_threat_2024} found the more precise the threat, the more credible it is deemed by public audiences. Moreover, the public tends to be skeptical of threats that are justified by the need to protect one’s national reputation. Interestingly, \textcite{kertzer_how_2021} also found that being an ally of the US increased perceptions of resolve, relative to being an adversary of the US. This finding seems to corroborate that being a member of an alliance increases the ability to bear costs in a confrontation, perhaps by reducing the risks of following through on threats. 

Anger has also been shown to influence audience perceptions of adversaries' resolve. \textcite{yoon_anger_2024} exposed respondents to a basic crisis scenario between the US and Russia and then measured baseline perceptions of the probability of Russia using force against the US and perceptions of how many causalities Russia's leader is willing to accept in order to win. These two outcome measures tap into public perceptions of an adversary's resolve. Respondents were then randomly assigned to receive an \textquote{anger} or \textquote{no anger} condition. In the anger condition, the Russian leader \textquote{explodes in rage} and \textquote{yells in outrage} that \textquote{we are angered by how America treated us,} whereas in the no anger condition, he \textquote{does not seem angry at all} and issues the threat \textquote{in a calm, measured voice.} The respondents answered the outcome questions again, testing whether anger affected the perceived probability of Russia following through on threats. The anger treatment made respondents 12\% more certain that Russia would use force against their country. The effect of anger was also calculated within-subjects, so the design is uniquely able to reveal how the anger treatment shifts perceptions of Russia's resolve and uncertainty within the same individuals. 

Yoon's design provides insight into whether angry threats are more credible at communicating an adversary's resolve in a way that the public can understand. However, it does not reveal whether the public becomes more supportive of staying out and deescalating the conflict. My interest is testing whether power asymmetry communicates resolve and suppresses support for retaliation. I argue that the perceived risk of threatening an adversary will rise as audience perceptions of power asymmetry increase.

\section{Design}
I propose a 3x2 design, varying power asymmetry along one dimension, and the presence of allied support on another dimension. This would amount to six total treatment conditions, if each cell were filled. At the moment, I have a budget for roughly n = 3000 respondents, which I will be recruiting with YouGov.\footnote{I reflect on my current challenges with case selection later on in this PAP.}

 \begin{table}[h]
  \centering
  \caption{3x2 Design}
  \label{tab:design}
  \begin{tabular}{cp{3cm}p{3cm}p{7cm}}
  \hline
  \textbf{Condition} & \textbf{Power (A)symmetry} & \textbf{Alliance Support} & \textbf{Expected Effect} \\
  \hline
  1 & Stronger adversary & Unified Ally Commitment    & Allied support may embolden the public to retaliate, but threats from a more powerful adversary may suppress retaliation. This condition represents the interaction between two opposing drivers. 
  \\
  2 & Stronger adversary & No Unified Ally Commitment & Reactance and the desire for retaliation should be suppressed, because of the high risks of retaliation and lack of allied support. \\
  3 & Equal power        & Unified Ally Commitment    & Reactance (desire to retaliate) is likely to surface here. Reactance may increase marginally in the presence of allied support (comparing Conditions 3 and 4).
   \\
  4 & Equal power        & No Unified Ally Commitment \\
  5 & Weaker adversary   & Unified Ally Commitment   &  A threat from a weak adversary should generate the strongest effect of reactance. Reactance may increase marginally in the presence of allied support (comparing Conditions 5 and 6).\\
  6 & Weaker adversary   & No Unified Ally Commitment \\
  \hline
  \end{tabular}
  \end{table}

However, I argue that in some cells, the additional treatment of allied support is unlikely to produce significantly different outcomes. Specifically, within the comparisons of Conditions 3 to 4 and Conditions 5 to 6, the presence of allied support may marginally increase support for retaliation. In keeping with \textcite{powers_psychology_2023}, the public will likely perceive threats from a weaker adversary to be less credible, thus making defiant support for retaliation a more likely outcome. I am considering collapsing Conditions 5 and 6 for this reason (and to preserve statistical power). However, given my interest in fielding this study outside of the United States, it is possible that public support for retaliation may be lower in general, even when receiving a threat from a weaker adversary. Thus, alliances may still play a significant role in generating support for retaliation against weak threats. 

\subsection{Hypotheses}
  \begin{table}[H]
  \centering
  \caption{Hypotheses and Treatment Comparisons}
  \label{tab:hypotheses}
  \footnotesize
  \begin{tabular}{lp{7cm}p{6cm}}
  \hline
  \textbf{Label} & \textbf{Hypothesis} & \textbf{Proposed Test} \\
  \hline
  H1a - Power Asymmetry  & Support for retaliation decreases as adversary power increases, and increases as adversary power decreases. & Compare marginal effect of power asymmetry across all ally conditions. \\
  H1b - Hawks & Among hawkish respondents, support for retaliation is suppressed when the adversary is more
  powerful. & Compare hawks across all power conditions. \\
  \hline
  H2  - Alliances & Ally support increases support for retaliation. & Compare the marginal effect of ally support across all power conditions. \\
  \hline
  Alternative 1 - Reactance & Threats from an adversary are perceived as \textbf{constraining}, which increases anger \textbf{and} support for retaliation, regardless of power asymmetry. & Use \textcite{powers_psychology_2023}'s anger measure to probe for reactance. \\
  Alternative 2 - Reputation & Threats from an adversary increase concerns for reputation costs \textbf{and} support for retaliation regardless of power asymmetry. &  Use \textcite{dafoe_coercion_2021}'s reputation measure to probe for reputation mechanism. \\
  \hline
  Exploratory - Resolve & Threats from a more powerful adversary are perceived to be more credible. & Use a pre-validated survey item of adversary resolve from \textcite{yoon_anger_2024, kertzer_how_2021} \\
  \hline
  \end{tabular}
  \end{table}


\subsection{Vignette Treatments (Draft)}
All respondents will first read an introductory text: 

\textit{
We are going to describe a situation our country has faced many times in the past 
and will probably face again in the future. We will ask for your opinion about how [TARGET COUNTRY] should handle a situation like the one described. Please read the details carefully and give thoughtful answers.}

Respondents will then read the following crisis scenario. Based on a randomization procedure, respondents will be assigned to one of the six treatment conditions. Based on the combinations set up in the 3x2 design, the manipulated information in the crisis scenario will vary along the hypothesized dimensions. 

\blockquote{
It is the year 2045. [TARGET COUNTRY] is involved in a tense standoff at sea with [ADVERSARY COUNTRY]. [POWER TREATMENT]. The
dispute began when [TARGET COUNTRY]'s navy intercepted and detained a vessel belonging to [ADVERSARY COUNTRY]. The vessel had disabled its maritime transponder and was found shadowing a [TARGET COUNTRY] naval patrol ship at close range.

[ADVERSARY COUNTRY] denied any wrongdoing. In response to the detainment, [ADVERSARY COUNTRY] deployed additional naval forces to the area and issued the following demand: If [TARGET COUNTRY] do not immediately release the vessel and crew, [ADVERSARY COUNTRY] will not hesitate to take military action to secure their release. 

The statement was broadcast in international news and prompted statements from [TARGET COUNTRY]'s allies. [ALLY TREATMENT].}


 \begin{table}[H]
  \centering
  \caption{Experimental Manipulations}
  \label{tab:manipulations}
  \begin{tabular}{p{3cm}p{3cm}p{7.5cm}}
  \hline
  \textbf{Dimension} & \textbf{Condition} & \textbf{Vignette Text} \\
  \hline
  \multirow{3}{3cm}{\textbf{Power Asymmetry}} & Stronger & [ADVERSARY COUNTRY] is a major military power whose armed forces are substantially larger and more capable than those of [TARGET COUNTRY]. \\[6pt]
   & Equal & [ADVERSARY COUNTRY] is a regional power whose armed forces are roughly equal in size and capability to those of [TARGET COUNTRY]. \\[6pt]
   & Weaker & [ADVERSARY COUNTRY] is a smaller power whose armed forces are substantially smaller and less capable than those of
  [TARGET COUNTRY]. \\
  \hline
  \multirow{2}{3cm}{\textbf{Alliance Support}} & Consensus & [TARGET COUNTRY]'s allies reached a formal consensus and
  made a collective commitment to providing military support to [TARGET COUNTRY] in this dispute. \\[6pt]
   & No consensus & [TARGET COUNTRY]'s allies have not reached a formal consensus, nor made a collective commitment to providing military support to [TARGET COUNTRY] in this dispute. \\
  \hline
  \end{tabular}
  \end{table}

\section{Case Selection}
For the purposes of this study, I need to select a case that is not a global superpower. This is essential in order to construct an ecologically valid test of whether power asymmetry has an effect on support for retaliation. However, I also need a case that contains considerable variation on foreign policy postures. A population whose strategic culture is dominated by consensus and non-intervention would not provide enough variation on hawkish attitudes, thus making it impossible to test for an interaction effect. At the same time, a population with more hawkish strategic attitudes would potentially skew the effects towards always standing firm regardless of power asymmetry or alliance consensus, thus resembling the reactance hypothesis. 

Moreover, the selection of my case will also affect which countries respondents plausibly associate with the power treatments. There are four possible approaches here. First, I could just use a generic placeholder, such as \textquote{a hostile country}. This approach resembles the bulk of experimental research on audience costs, which relies on similar vignette crisis scenarios. \autocite{herrmann_mass_1999, tomz2007, kertzer_decomposing_2016} As a sanity check, these studies often also ask respondents to identify which country they may have been thinking of at the end of the experiment. 

Second, I could create a fictional country (Powers and Altman use \textit{Navalia}, Davies and Johns use \textit{Nizwar}).\autocite{powers_psychology_2023, davies_audience_2013} The benefit of this approach is that respondents will not have any priors about the country's reputation for resolve, nor the country's military capacity, strengthening the causal identification of the power treatment. Furthermore, by setting the scenario in the future, I can try to improve the plausibility of the fictional country making such a threat.  

Third, I could select real countries with real hostilities towards the target country. \textcite{dafoe_coercion_2021, dafoe_provocation_2022} use specific and realistic examples of disputes between China and the United States, while \textcite{yoon_anger_2024} pitches a future dispute between Russia and the United States. The benefit of this approach is both internal and ecological validity. The realism of both disputes strengthen the plausibility of the treatments, and ensure that the effects on perceived resolve and reputational damage are likely generalizable outside of the experimental setting. However, this approach is particularly tricky in my 3x2 design, because I would need to select three countries that match the three different power dimensions vis a vis my target country. 

Finally, I can switch from a design-based treatment to a sample-based treatment. I would have to start with a plausible adversary (say, Russia) and select samples of respondents from a relatively weaker country, a relatively equal country, and a relatively stronger country. This is arguably the most risky approach, because it relinquishes all the leverage of power asymmetry to my own assumptions about how respondents a selected country perceive their relative power to Russia. 

This is one of my current challenges, and I look forward to receiving your suggestions!


\section{Draft Questionnaire}

 \begin{enumerate}
      \item Pre-Treatment Demographic Variables:
      \begin{enumerate}
          \item Age
          \item Gender
          \item Ideology on a left-right scale
          \item Partisanship (either retrospective or prospective vote choice)
          \item Political Interest
          \item Education level
          \item Foreign Policy Postures:
          \begin{enumerate}
              \item \emph{Isolationism 1}: The interests of [my country] and its people are best protected by avoiding involvement with other nations.
              \item \emph{Isolationism 2}: [My country] needs to simply mind its own business when it comes to international affairs.
              \item \emph{Militant Internationalism 1}: [My country] should take all steps including the use of force to prevent aggression by any expansionist power.
              \item \emph{Militant Internationalism 2}: [My country] needs a strong military to be effective in international relations.
              \item \emph{Cooperative Internationalism 1}: When deciding its foreign policies, [my country] should take into account the views of its major allies.
              \item \emph{Cooperative Internationalism 2}: [My country] should be more committed to diplomacy and not so fast to use the military in international crises.
          \end{enumerate}
      \end{enumerate}
      \item VIGNETTE BLOCK
      \item Manipulation Checks\footnote{Some of these are \textbf{must} haves, others are just nice to have} (Random Order):
      \begin{enumerate}
      \item In the scenario you read, did [ADVERSARY COUNTRY] \textbf{directly demand} something from [TARGET COUNTRY]?
      \begin{enumerate}
          \item Yes
          \item No
          \item They asked for something, but did not demand it
          \item I don't know 
      \end{enumerate} 
          \item Which of the following best describes the [ADVERSARY COUNTRY]'s behavior towards [TARGET COUNTRY] in the scenario?
          \begin{enumerate}
              \item {}[ADVERSARY] minded its own business
              \item {}[ADVERSARY] was taking risks, but did nothing wrong
              \item {}[ADVERSARY] was trying to test [TARGET COUNTRY]
              \item {}[ADVERSARY] was trying to harm [TARGET COUNTRY]
          \end{enumerate}
          \item Given the information available in this scenario, do you think one of the countries has \textbf{superior military capabilities}, or are they \textbf{equal}?
          \begin{enumerate}
              \item {}[ADVERSARY] is stronger
              \item {}[ADVERSARY] and [TARGET] are equal
              \item {}[TARGET] is stronger
          \end{enumerate}
          \item On a scale ranging from 0 to 100\%, how \textbf{confident} are you that [TARGET COUNTRY]'s allies would lend support in the event that the conflict escalates?
          \item Given the information available, what is your best estimate about whether [ADVERSARY COUNTRY] will \textbf{follow through on its threats}, ranging from 0 to 100\%?
      \end{enumerate}
      \item Main Outcomes:
      \begin{enumerate}
          \item \textbf{Comply or Defy:} What do you think [TARGET COUNTRY] should do in response to [ADVERSARY COUNTRY]'s ultimatum?
            \begin{enumerate}
              \item 1- Release the vessel and crew immediately 
              \item 2- Continue holding the vessel 
            \end{enumerate}
            \item On a scale from 0-10, how strongly do you feel about this choice?
            \item \textbf{Support for Retaliation} If [TARGET COUNTRY] were to defy [ADVERSARY]'s ultimatum, to what extent would you support or oppose each of the following approaches? (Random order, 5-point scale from "Strongly support" to "Strongly oppose")
            \begin{enumerate}
                \item Try to deescalate through diplomatic channels, without taking any military action
                \item Impose economic sanctions against [ADVERSARY COUNTRY]
                \item Deploy additional naval forces to confront [ADVERSARY COUNTRY]'s vessels in the area
                \item Conduct a military strike against [ADVERSARY COUNTRY]'s naval forces
            \end{enumerate}
            \item \textbf{Open-Ended Response}: In a few words, please explain why you think [TARGET COUNTRY] should follow that approach.
      \end{enumerate}
      \item Secondary Outcomes\footnote{Some of these are \textbf{must} haves, others are just nice to have}:
      \begin{enumerate}
       \item \textbf{National Resolve}: If the conflict escalates, how confident are you on a scale of 0-10 that [TARGET COUNTRY] will stand firm against [ADVERSARY COUNTRY]'s ultimatum?
         \item \textbf{Emotions Battery}: Please indicate your feelings toward [ADVERSARY COUNTRY] when thinking about this situation. To what extent do you feel...(presented in random order, thermometer scale 0 "not at all" — 10 "very")
         \begin{enumerate}
            \item \textbf{Angry} [anger scale]
            \item Furious [anger scale]
            \item Annoyed [anger scale]
            \item \textbf{Anxious} [fear]
            \item Worried [fear]
            \item Sad [distractor]
            \item Happy [distractor]
         \end{enumerate}
          \item \textbf{Reputation Battery}: To what extent do you agree or disagree with the following statements? (Random order, 5-point scale from "Strongly disagree" to "Strongly agree")
          \begin{enumerate}
              \item The events in this scenario put [TARGET COUNTRY]'s international reputation at stake
              \item {}[ADVERSARY COUNTRY] humiliated [TARGET COUNTRY]
              \item {} Agreeing to the ultimatum now would invite more threats to [TARGET COUNTRY]'s security in the long-run
              \item {} Agreeing to the ultimatum now would avoid the risk of war with [ADVERSARY COUNTRY] (reverse-coded)
          \end{enumerate}
          \item \textbf{Reactance Battery}: To what extent do you agree or disagree with the following statements? (Random order, 5-point scale from "Strongly disagree" to "Strongly agree")
          \begin{enumerate}
            \item {}[ADVERSARY COUNTRY] tried to make a decision for [TARGET COUNTRY]
            \item {}[ADVERSARY COUNTRY] tried to pressure [TARGET COUNTRY]
            \item {}[ADVERSARY COUNTRY] tried to take away [TARGET COUNTRY]'s freedom to choose how to respond
          \end{enumerate}
      \end{enumerate}
  \end{enumerate}


\printbibliography

\end{document}